Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-08 ms/manuscript.Rmd
Separate out references in Table 1 into their own column

# Write out table in rich text format for submitting
# MS as word doc
traits_used %>%
  gt %>%
  fmt_markdown(columns = everything()) %>%
  gt(rowname_col = "trait") %>%
  tab_row_group(
    group = "Sporophyte traits",
    rows = matches("Stipe|Frond|Rhizome|Pinna|Leaf")
  ) %>%
  tab_row_group(
    group = "Gametophyte traits",
    rows = matches("Morphotype|Gemmae|Glands|Hairs")
  ) %>%
  cols_label(
    data_type = "Data type (unit)",
    ecological_significance = "Ecological Significance"
  ) %>% 
  as_rtf() %>%
  write_lines(here("ms/table1.rtf"))

# Include in PDF using kableExtra to convert to latex format
traits_used %>% 
  rename(`Data type (unit)` = data_type, `Functional significance` = ecological_significance) %>%
  column_to_rownames("trait") %>%
  knitr::kable(caption = "Traits used in this study", format = "latex", booktabs = TRUE, escape = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  pack_rows("Sporophyte traits", 1, 7) %>%
  pack_rows("Gametophyte traits", 8, 11) %>%
  column_spec(3, width = "15em") %>%
  footnote(general = "References: 1, Watkins \\\\textit{et al.} (2010); 2, Vogel (1968); 3, Creese \\\\textit{et al.} (2011); 4, Kluge \\\\& Kessler (2007); 5, Wright \\\\textit{et al.} (2004); 6, Watkins \\\\textit{et al.} (2007b); 7, Pittermann \\\\textit{et al.} (2013); 8, Farrar \\\\textit{et al.} (2008); 9, Wollenweber \\\\& Schneider (2000). Noncordate gametophyte morphotypes include ribbon, strap and filamentous.", general_title = "", threeparttable = TRUE, escape = FALSE)
```

>>>>

# Write out table in rich text format for submitting
# MS as word doc
traits_used %>%
  gt %>%
  fmt_markdown(columns = everything()) %>%
  gt(rowname_col = "trait") %>%
  tab_row_group(
    group = "Sporophyte traits",
    rows = matches("Stipe|Frond|Rhizome|Pinna|Leaf")
  ) %>%
  tab_row_group(
    group = "Gametophyte traits",
    rows = matches("Morphotype|Gemmae|Glands|Hairs")
  ) %>%
  cols_label(
    data_type = "Data type (unit)",
    ecological_significance = "Ecological Significance",
    reference = "Reference(s)"
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/table1.rtf"))

# Include in PDF using kableExtra to convert to latex format
traits_used %>% 
  rename(`Data type (unit)` = data_type, `Functional significance` = ecological_significance, `Reference(s)` = reference) %>%
  column_to_rownames("trait") %>%
  knitr::kable(caption = "Traits used in this study", format = "latex", booktabs = TRUE, escape = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  pack_rows("Sporophyte traits", 1, 7) %>%
  pack_rows("Gametophyte traits", 8, 11) %>%
  column_spec(2, width = "8em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "8em") %>%
  footnote(general = "Noncordate gametophyte morphotypes include ribbon, strap and filamentous.", general_title = "", threeparttable = TRUE, escape = TRUE)
```
